Submission 1.1

### 2023-08-23 Submission 1.1.tex
Fixed quote marks

\begin{enumerate}
      \item Knaves always lie, knights always tell the truth, and in Transylvania, where everybody is one or the other (but you can't tell which by looking), you encounter two people, one of whom says, “He's a knight or I'm a knave.” What are they? (J 20)\\\\
            A: I'm a knight.\\
            B: He's a knight.\\
            C: He's a knight or I'm a knave.\\
            Notes:\\
            If being a knight is false, being a knave is true.\\
            If I am a knight, then (he's a knight or I'm not a knight). If I'm not a knight, then not (he's a knight or I'm not a knight).\\
            To solve the problem, we must find a combination of knight and knave such that the truth value of "he's a knight or I'm a knave" is consistent with whether or not I'm a knight. Therefore, we're searching for a value where C and A are equivalent.\\
            \begin{tabular}{c|c|c|c}
                  A & B & $C: B \lor \neg A$ & $A \leftrightarrow C$ \\
                  \hline
                  T & T & T                  & T                     \\
                  T & F & F                  & F                     \\
                  F & T & T                  & F                     \\
                  F & F & T                  & F                     \\
            \end{tabular}
            Both he and I are knights.
\end{enumerate}

@@

                        $A \to B$\\
                        $C \to A$\\
                        \rule{5em}{.5pt}\\
                        $C \to B$
                  \item
                        \begin{tabular}{c|c|c|c|c}
                              A                      & B & C & $A \to B$ & $C \to A$ \\
                              T                      & T & T & T         & T         \\
                              T                      & T & F & T         & T         \\
                              \rowcolor{lightgray} T & F & T & F         & T         \\
                              \rowcolor{lightgray} T & F & F & F         & T         \\
                              \rowcolor{lightgray} F & T & T & T         & F         \\
                              F                      & T & F & T         & T         \\
                              \rowcolor{lightgray} F & F & T & T         & F         \\
                              F                      & F & F & T         & T         \\
                        \end{tabular} \\ In the rows where both premises are met, there is only one case where Brown dies before the election, and in this case he does indeed retire to private life. This means the argument is valid.
            \end{enumerate}
      \item "Thin is guilty," observed Watson, “because either Holmes is right and the vile Moriarty is guilty or he is wrong and the scurrilous Thin did the job; but those scoundrels are either both guilty or both innocent; and, as usual, Holmes is right.” (J 18)
            \begin{enumerate}[(a)]
                  \item Holmes is right or wrong.\\
                        If Holmes is right, Moriarty is guilty.\\
                        If Holmes is wrong, Thin is guilty.\\
                        Moriarty and Thin are either both guilty or both innocent (i.e. If Moriarty is guilty, Thin is guilty).\\
                        \rule{15em}{.5pt}\\
                        Thin is guilty.
                  \item The argument is valid. Soundness is difficult to determine.
                  \item \textit{A}: Holmes is right.\\
                        \textit{B}: Moriarty is guilty.\\
                        \textit{C}: Thin is guilty.\\

@@

            \textit{Saffron's Commentary: I don't really know what contingent means! It's defined in the textbook, but I don't know if this question means "C is contingent upon $A \land B$" or simply "$(A \land B) \to C$" may be true or untrue depending on the case. I'm assuming the latter for this problem, but who knows.

>>>>

\begin{enumerate}
      \item Knaves always lie, knights always tell the truth, and in Transylvania, where everybody is one or the other (but you can't tell which by looking), you encounter two people, one of whom says, “He's a knight or I'm a knave.” What are they? (J 20)\\\\
            A: I'm a knight.\\
            B: He's a knight.\\
            C: He's a knight or I'm a knave.\\
            Notes:\\
            If being a knight is false, being a knave is true.\\
            If I am a knight, then (he's a knight or I'm not a knight). If I'm not a knight, then not (he's a knight or I'm not a knight).\\
            To solve the problem, we must find a combination of knight and knave such that the truth value of “he's a knight or I'm a knave” is consistent with whether or not I'm a knight. Therefore, we're searching for a value where C and A are equivalent.\\
            \begin{tabular}{c|c|c|c}
                  A & B & $C: B \lor \neg A$ & $A \leftrightarrow C$ \\
                  \hline
                  T & T & T                  & T                     \\
                  T & F & F                  & F                     \\
                  F & T & T                  & F                     \\
                  F & F & T                  & F                     \\
            \end{tabular}
            Both he and I are knights.
\end{enumerate}

@@

                        $A \to B$\\
                        $C \to A$\\
                        \rule{5em}{.5pt}\\
                        $C \to B$
                  \item
                        \begin{tabular}{c|c|c|c|c}
                              A                      & B & C & $A \to B$ & $C \to A$ \\
                              T                      & T & T & T         & T         \\
                              T                      & T & F & T         & T         \\
                              \rowcolor{lightgray} T & F & T & F         & T         \\
                              \rowcolor{lightgray} T & F & F & F         & T         \\
                              \rowcolor{lightgray} F & T & T & T         & F         \\
                              F                      & T & F & T         & T         \\
                              \rowcolor{lightgray} F & F & T & T         & F         \\
                              F                      & F & F & T         & T         \\
                        \end{tabular} \\ In the rows where both premises are met, there is only one case where Brown dies before the election, and in this case he does indeed retire to private life. This means the argument is valid.
            \end{enumerate}
      \item “Thin is guilty,” observed Watson, “because either Holmes is right and the vile Moriarty is guilty or he is wrong and the scurrilous Thin did the job; but those scoundrels are either both guilty or both innocent; and, as usual, Holmes is right.” (J 18)
            \begin{enumerate}[(a)]
                  \item Holmes is right or wrong.\\
                        If Holmes is right, Moriarty is guilty.\\
                        If Holmes is wrong, Thin is guilty.\\
                        Moriarty and Thin are either both guilty or both innocent (i.e. If Moriarty is guilty, Thin is guilty).\\
                        \rule{15em}{.5pt}\\
                        Thin is guilty.
                  \item The argument is valid. Soundness is difficult to determine.
                  \item \textit{A}: Holmes is right.\\
                        \textit{B}: Moriarty is guilty.\\
                        \textit{C}: Thin is guilty.\\

@@

            \textit{Saffron's Commentary: I don't really know what contingent means! It's defined in the textbook, but I don't know if this question means “C is contingent upon $A \land B$” or simply “$(A \land B) \to C$” may be true or untrue depending on the case. I'm assuming the latter for this problem, but who knows.
